Party tricks for PostgreSQL \\ perf, ftrace and bpftrace

### 2022-10-25 pgconfeu2022/presentation.tex
Adjustments

    %\vspace*{1.5em}
    \fontsize{8pt}{10}\selectfont
    {\begin{flushleft}\color{black} 24-09-2022\end{flushleft}}%

@@

\renewcommand\UrlFont{\color{gray!50}\rmfamily\itshape}
\begin{frame}
    \frametitle{}
    \begin{center}
        \copyrightbox[b]
            {\includegraphics[width=0.9\textwidth,center]{more.png}}
            {Belzebubs: \url{belzebubsofficial.tumblr.com}}
    \end{center}
\end{frame}
\note{
    Copyright, link
}

@@

\begin{frame}
    \frametitle{}
    \begin{center}
        \copyrightbox[b]
            {\includegraphics[width=0.7\textwidth,center]{elephant.jpg}}
            {Dmitrii Dolgov: Teufelsberg, Berlin}

    \end{center}
\end{frame}
\note{
    Copyright, name place
}

>>>>

    %\vspace*{1.5em}
    \fontsize{8pt}{10}\selectfont
    {\begin{flushleft}\color{black} 26-10-2022\end{flushleft}}%

@@

\renewcommand\UrlFont{\color{gray!50}\rmfamily\itshape}
\begin{frame}
    \frametitle{}
    \begin{center}
        \copyrightbox[b]
            {\includegraphics[width=0.9\textwidth,center]{more.png}}
            {Belzebubs: \url{belzebubsofficial.tumblr.com}}
    \end{center}
\end{frame}

@@

\begin{frame}
    \frametitle{}
    \begin{center}
        \copyrightbox[b]
            {\includegraphics[width=0.7\textwidth,center]{elephant.jpg}}
            {Photo by Dmitrii Dolgov: Teufelsberg, Berlin}

\renewcommand\UrlFont{\color{black}\rmfamily}
\begin{frame}[fragile]{}
    \frametitle{}
    \begin{center}
        \begin{itemize}[label={}]
            \item {\url{postgresql.org/docs/current/dynamic-trace.html}}
            \item {\url{perf.wiki.kernel.org/index.php/Tutorial}}
            \item {\url{kernel.org/doc/Documentation/trace/ftrace.txt}}
            \item {\url{github.com/iovisor/bpftrace}}
            \item {Gregg, Brendan. "Systems Performance: \\ Enterprise and the Cloud"}
        \end{itemize}
    \end{center}
\end{frame}
